### 2025-06-01 conteudo/methods/methods.tex
fix IIO subsystem

The ethnographic study had two phases. In the first phase, the author explored the process 
of mitigating a code duplication found in the AMD Display driver and sent it as a PATCH to 
interact with the Linux community and get their feedback. In the second phase, we proposed 
to students in the course Free Software Development at the University of São Paulo to mitigate 
the code duplications found by the tool in the IIO subsystems and the AMD Display driver and 
pass the process of sending the mitigations as PATCH.

>>>>

The ethnographic study had two phases. In the first phase, the author explored the process 
of mitigating a code duplication found in the AMD Display driver and sent it as a PATCH to 
interact with the Linux community and get their feedback. In the second phase, we proposed 
to students in the course Free Software Development at the University of São Paulo to mitigate 
the code duplications found by the tool in the IIO subsystem and the AMD Display driver and 
pass the process of sending the mitigations as PATCH.

### 2025-06-01 conteudo/results/participant.tex
fix IIO subsystem

The initial plan of this research was to approach and send many mitigations to collect 
many artifacts from the driver community. Still, the slow process of sending a patch 
makes this plan unviable. Thus, we opted to redirect this research to work with students 
and refactoring duplicated function pairs found by the tool directly in the IIO and the 
AMD Display driver without passing through the whole process of the systematic approach 
proposed. This alternative allowed us to collect artifacts from the students' experiences 
and findings and not be too dependent on the interaction with the kernel community. 
Another advantage is accelerating the interaction with the kernel community because we are 
not applying the systematic approach, which translates to more minor code changes.

>>>>

The initial plan of this research was to approach and send many mitigations to collect 
many artifacts from the driver community. Still, the slow process of sending a patch 
makes this plan unviable. Thus, we opted to redirect this research to work with students 
and refactoring duplicated function pairs found by the tool directly in the IIO subsystem and the 
AMD Display driver without passing through the whole process of the systematic approach 
proposed. This alternative allowed us to collect artifacts from the students' experiences 
and findings and not be too dependent on the interaction with the kernel community. 
Another advantage is accelerating the interaction with the kernel community because we are 
not applying the systematic approach, which translates to more minor code changes.

### 2025-06-01 conteudo/results/students.tex
fix IIO subsystem

For the students who worked in the IIO subsystems, we gave them duplicated function pairs 
found by the tool, and their responsibility was to think of how to mitigate the duplication 
and send the patch to the maintainers. The student that worked in the AMD Display driver 
have the additional work to use the tool to find the duplications.

Appendix \ref{app:stuart} has references to the artifacts discussed in this section, 
including the duplication function pairs that students mitigate, the students’ reports, 
the patch students sent to the Linux kernel, and the answers to the questionnaire asked 
of the students who worked in the AMD Display driver and the teaching assistant that used 
the tool to find duplications in the IIO.

>>>>

For the students who worked in the IIO subsystem, we gave them duplicated function pairs 
found by the tool, and their responsibility was to think of how to mitigate the duplication 
and send the patch to the maintainers. The student that worked in the AMD Display driver 
have the additional work to use the tool to find the duplications.

Appendix \ref{app:stuart} has references to the artifacts discussed in this section, 
including the duplication function pairs that students mitigate, the students’ reports, 
the patch students sent to the Linux kernel, and the answers to the questionnaire asked 
of the students who worked in the AMD Display driver and the teaching assistant that used 
the tool to find duplications in the IIO subsystem.
